Flatiron analysis

### 2021-09-15 Rmd/Report 2021.Rmd
Update code

## Patients with a date of drug or date of surgery BEFORE diagnosis will be excluded
```{r drugs episode cleanup}
drugs1 <- drugs %>% 
  filter(episodedatasource == "Administrations" & 
           ismaintenancetherapy == "FALSE") %>%
  # 1. 60 days rule between diagnosis and treatment # Loss 1
  # bind with clinical
  inner_join(., clinical_data, #%>% select("patientid", "diagnosisdate", "surgerydate"),
          by = "patientid") %>% 
  arrange(patientid, episodedate) %>% 
  group_by(patientid) %>% 
  mutate(first_drug_date = first(episodedate)) %>% 
  mutate(days_at_first_drug = interval(start = diagnosisdate, end = first_drug_date)/
           duration(n=1, units = "months")) %>% 
  mutate(days_at_surg = interval(start = diagnosisdate, end = surgerydate)/
           duration(n=1, units = "months")) %>% 
  ungroup()

drugs1 %>% filter(days_at_first_drug < 0) %>% distinct(patientid) %>% nrow()
drugs1 %>% filter(days_at_surg < 0) %>% distinct(patientid) %>% nrow()
```

@@

## 60 days rule between diagnosis and treatment
60 days rule between diagnosis and treatment to eliminate patients who didn't get treatment for 60 days which could mean they were treated but it is not recorded 
```{r}
remove_60daysrule <- drugs1 %>% 
  filter((days_at_first_drug > 60 | days_at_surg > 60)) %>% 
  distinct(patientid)
remove_60daysrule <- paste(remove_60daysrule$patientid, collapse = "|")

@@

Remove linename that doesn't include platin or taxels -> later in the process, need first to recode linenumber with all the drugs in.
```{r}
# drugs1 <- drugs1 %>% 
#   # 2. Filtering----
#   filter(episodedatasource == "Administrations" & 
#            # ismaintenancetherapy == "FALSE" & 
#            !is.na(amount) &
#            (days_at_first_drug < 60 | days_at_surg < 60) &
#            
#            days_at_first_drug >= 0 &
#            (is.na(surgerydate) | days_at_surg >= 0)
#          )

@@

## Combine multiple administrations of the same drug at the same date
```{r combine amount same drug one day}
drugs1 <- drugs1 %>% 
  #When want to remove patients who didn't have taxel/platin as 1st line -> remove 260 patients
  # filter(!(linenumber == 1 & !str_detect(linename, "taxel|platin"))) %>% 
  # filter(str_detect(drugname, "taxel|platin") & str_detect(route, "venous|peritoneal")) %>% ############## LATER------------!!!!!
  select(-c(enhancedcohort, episodedatasource, drugcategory, detaileddrugcategory, route)) %>%

@@

## Recode linenumber depending on surgery date (Categorize Neo and Adjuavnt)
```{r line coding}
therapy_line <- drugs1 %>% 
  # 4. Define Adjuvant, Neoadjuvant, chemo or surgery----
  mutate(chemotherapy_type = case_when(
    # ismaintenancetherapy == "TRUE"    ~ "maintenance",
    episodedate <= surgerydate        ~ "Neoadjuvant", # F63ABD6AEB12C, F4F7B1C5DF24F intraperitoneal Carboplatin
    episodedate > surgerydate         ~ "Adjuvant",
    is.na(surgerydate) &
      !is.na(episodedate)             ~ "Chemotherapy only",
    !is.na(surgerydate) &
      is.na(episodedate)              ~ "Surgery only"
    )) %>% 
  mutate(chemotherapy_type = factor(chemotherapy_type, levels = c("Neoadjuvant", "Adjuvant", "Chemotherapy only", "Surgery only"))) %>%
  group_by(patientid) %>% 
  mutate(had_neo = ifelse(str_detect(chemotherapy_type, "Neo"), "Yes", NA_character_)) %>% 
  fill(had_neo, .direction = "updown") %>% 
  mutate(had_adj = ifelse(str_detect(chemotherapy_type, "Adj"), "Yes", NA_character_)) %>% 
  fill(had_adj, .direction = "updown") %>% 
  mutate(treatment_sequence = case_when(
    had_neo == "Yes" &
      had_adj == "Yes"                           ~ "neo + surg + adj",
    had_neo == "Yes" &
      is.na(had_adj)                             ~ "neo + surg",
    is.na(had_neo) &
      had_adj == "Yes"                           ~ "surg + adj",
    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
    chemotherapy_type == "Surgery only"          ~ "Surgery only"
  )) %>% 
  mutate(therapy = case_when(
    chemotherapy_type == "Neoadjuvant"           ~ "Upfront Chemo",
    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
    chemotherapy_type == "Surgery only"          ~ "Surgery only",
    is.na(had_neo) &
      had_adj == "Yes"                           ~ "Upfront Surgery"
  )) %>% 
  fill(therapy, .direction = "downup") %>% 
  # mutate(therapy1 = case_when(
  #   chemotherapy_type == "Adjuvant"              ~ "Upfront Surgery",
  # )) %>% 
  # fill(therapy1, .direction = "downup") %>% 
  # mutate(therapy = coalesce(therapy, therapy1)) %>% 
  # select( -therapy1) %>%

@@

## Number of patient who switch line because of surgery from line 1 to adjuvant line
```{r Number of patient who switch line}
therapy_line %>% 
  mutate(change_line = case_when(
    linenumber == 1 & 
      linenumber_new == 2 &
      chemotherapy_type == "Adjuvant" &
      treatment_sequence == "neo + surg + adj"     ~ 1,
    TRUE                                           ~ 0
  )) %>% 
  arrange(desc(change_line)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(change_line) %>% 
  tbl_summary()
```
## Here I want to plot the lengh of the line 1 which got brought to Adjuvant...

## How many lines patient got as Neo
```{r}
therapy_line %>% 
  filter(chemotherapy_type == "Neoadjuvant") %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new) %>% 
  tbl_summary()

@@

## Remove patients with more than 1 line as Neo -34
```{r}
remove_morethan1_neo <- therapy_line %>% 
  filter(chemotherapy_type == "Neoadjuvant" &
           linenumber_new != 1)
remove_morethan1_neo <- paste(remove_morethan1_neo$patientid, collapse = "|")

@@

## Remove patients who switch cispl vs carbo # 111 patients Car > Cis F1BF7208F0E96, 34 Cis > Car in neo or adj or chemo
```{r}
# But a lot switch cispl vs carbo # 59 patients Car > Cis F1BF7208F0E96, 32 Cis > Car
therapy_line %>% 
  filter(str_detect(linename, "Car") &
           drugname == "cisplatin") %>%
  distinct(patientid) %>% nrow()

@@

Should I do the same between paclitaxel and docetaxel? Remember I pacli == pacli protein bound

If a patient had carbo, pacli, carbo, pacli, docetaxel in a Cabo-Pacli line : Could be annoying when I code cycle

In 1 cycle we can have taxel multiple times, is it possible for carbo or cisplatin?
```{r}
# But a lot switch cispl vs carbo # 59 patients Car > Cis F1BF7208F0E96, 32 Cis > Car
therapy_line %>% 
  filter(str_detect(linename, "Pacli") &
           drugname == "docetaxel") %>%
  distinct(patientid) %>% nrow()
therapy_line %>% 
  filter(str_detect(linename, "Doce") &
           drugname == "Paclitaxel") %>%
  distinct(patientid) %>% nrow()
```

## Code cycle
```{r cycle coding}
# Code cycle number
therapy_cycle <- therapy_line %>%

@@

## Bind everything together and calculating target_auc and expected dose

When I bind things together I take the closest date of creatinine, height, weight, BSA, AUC, from the cycle date to calculate `target_auc` and `expected_dose`. it can be days in between or more. Do we need a max?
Precision when binding for AUC I bind the closest with corresponding drugname (Pacli AUC is not bind with Carbo drug)
```{r target_auc and expected dose}
Treatment <- 
  # Merge with creatinine
  left_join(therapy_cycle, creatinine, by = "patientid") %>%
  mutate(interval_creat = abs(interval(start= creat_date, end= cycle_start_date)/                      
                          duration(n=1, unit="days"))) %>% 
  arrange(interval_creat) %>% 
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
           cycle_start_date, .keep_all = TRUE) %>%

@@

## Exclude exclude == "1" coded by Lauren due to Flatiron rule

@@

@@

```{r}
Frontline <- Treatment %>% 
  # filter(therapy == "Upfront Chemo" | therapy == "Chemotherapy only") %>% 
  # group_by(patientid, linenumber_new, cycle_increment, drugname) %>% # ! -----------------------Change drugname if combine taxel....
  # mutate(amount_cycle = sum(amount)) %>% 
  # select(patientid, linenumber_new, cycle_increment, drugname, amount, amount_cycle, 
  #        target_auc, expected_dose, everything()) %>% # F01E4E6DD63C5, F1FA39C41A087 ----------- No we have xpected dose for each episode
  # ungroup() %>% 
  # distinct(patientid, linenumber_new, cycle_increment, drugname, .keep_all = TRUE) %>%

  # Create a linenumber restating at 1 for adj to be able to calculate RDI for first line of Adjuvant
    group_by(patientid, chemotherapy_type) %>% 
  mutate(linenumber_adj = dense_rank(linenumber_new)) %>%

  # Calculate 1 RDI per drug per day, for whole Neoadjuvant and for first line of Adjuvant
  mutate(relative_dose_intensity = case_when(
    chemotherapy_type == "Adjuvant" &
      linenumber_adj == 1                  ~ amount/expected_dose,
    chemotherapy_type == "Neoadjuvant"     ~ amount/expected_dose
  )) %>%
  # select(patientid, linenumber_new, chemotherapy_type, drugname_type, drugname,
  #        relative_dose_intensity, linenumber_adj) %>%

  # Average RDI by taxel or platin by line (will combine pacli-doce and cis-carbo-oxalo)
  group_by(patientid, chemotherapy_type, drugname_type) %>%
  mutate(mean_RDI_per_chemotype_drug = case_when(
    chemotherapy_type == "Adjuvant" &
      linenumber_adj == 1                  ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3),
    chemotherapy_type == "Neoadjuvant"     ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  )) %>% 
  ungroup() %>%

  # Then let's see if we need to average that for the whole Neo BUT 
  # For now average rdi over whole neo, average rdi for the first line over adjuvant
  # when plot meed 1 rdi per drugname_type per chemotherapy_type aka distinct(patientid, chemotherapy_type, drugname_type)

  # group_by(patientid, chemotherapy_type, drugname_type) %>% 
  # mutate(RDI_neo = case_when(
  #   # chemotherapy_type == "Adjuvant"       ~ first(mean_RDI_per_drug_line), # F002B429BE6C6
  #   chemotherapy_type == "Adjuvant" &
  #     linenumber_adj == 1                  ~ mean(mean_RDI_per_drug_line),
  #   chemotherapy_type == "Neoadjuvant"     ~ mean(mean_RDI_per_drug_line) # F0040EA299CF0
  # )) %>%

  # mutate(RDI_adj = case_when(
  #   chemotherapy_type == "Adjuvant" &
  #     linenumber_adj == 1                  ~ mean(mean_RDI_per_drug_line), # F002B429BE6C6
  #   # chemotherapy_type == "Neoadjuvant"     ~ mean(mean_RDI_per_drug_line) # F0040EA299CF0
  # )) %>% 
  # mutate(RDI = coalesce(RDI_neo, RDI_adj))

  # group_by(patientid, chemotherapy_type, drugname) %>% # ------------------------ Or should I do by cycle, then avg again
  # mutate(mean_RDI_per_drug_chemotype = mean(relative_dose_intensity)) %>% 
  # ungroup() %>% 
  mutate(RDI_grp = as.factor(findInterval(mean_RDI_per_chemotype_drug, c(0.85) ))) %>% 
  mutate(RDI_grp = factor(RDI_grp, 
                           levels = c("1", "0"), 
                           labels = c("RDI >= 0.85", "RDI < 0.85"))) %>% 
  mutate(RDI_grp1 = as.factor(findInterval(mean_RDI_per_chemotype_drug, c(0.75, 0.85, 1, 1.5, 2) ))) %>% 
  mutate(RDI_grp1 = factor(RDI_grp1, 
                          levels = c("3", "0", "1","2","4", "5"), 
                          labels = c("0.85 >= RDI < 1", "0 < RDI < 0.75", "0.75 <= RDI < 0.85", "1 <= RDI < 1.5", 
                                     "1.5 <= RDI < 2", "RDI >= 2"))) %>% 
  # mutate(delay_incare_dx_to_treat = case_when(
  #   str_detect(therapy, "Chemo")     ~ (interval(start = diagnosisdate, end = episodedate)/
  #     duration(n=1, units = "days")),
  #   str_detect(therapy, "Surgery")   ~ (interval(start = diagnosisdate, end = surgerydate)/
  #     duration(n=1, units = "days"))
  # )) %>% 
  # group_by(patientid) %>% 
  # mutate(first_treatment_date = case_when(
  #   treatment_sequence == "Chemotherapy only"             ~ min(episodedate),
  #   str_detect(treatment_sequence, "neo")                 ~ min(episodedate),
  #   treatment_sequence == "surg + adj"                    ~ surgerydate,
  #   treatment_sequence == "Surgery only"                  ~ surgerydate
  # )) %>% 
  group_by(patientid) %>% 
  mutate(first_treatment_date = case_when(
    str_detect(therapy, "Chemo")                      ~ min(episodedate),
    str_detect(therapy, "Surgery")                    ~ surgerydate,
  )) %>% 
  mutate(delay_incare_dx_to_treat = interval(start = diagnosisdate, end = first_treatment_date)/
                                          duration(n=1, units = "days")) %>% 
  mutate(month_at_os_from_treatment = interval(start = first_treatment_date, end = followupdate)/
                   duration(n=1, units = "months")) %>% 
  ungroup() %>% 
  # %>% 
  # select(patientid, linenumber_new, drugname, surgerydate, episodedate, treatment_sequence, first_treatment_date, month_at_os_from_treatment)
  mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/
           duration(n=1, units = "days"), 
         thirty_days_exclusion = ifelse(thirty_days_exclusion <= 30, "Exclude", NA_character_))

>>>>

### step 1: Patients with a date of drug or date of surgery BEFORE diagnosis will be excluded
```{r drugs episode cleanup}
drugs1 <- drugs %>% 
  filter(episodedatasource == "Administrations" & 
           ismaintenancetherapy == "FALSE") %>%
  # 1. 60 days rule between diagnosis and treatment # Loss 1
  # bind with clinical
  inner_join(., clinical_data, #%>% select("patientid", "diagnosisdate", "surgerydate"),
          by = "patientid") %>% 
  arrange(patientid, episodedate) %>% 
  group_by(patientid) %>% 
  mutate(first_drug_date = first(episodedate)) %>% 
  mutate(days_at_first_drug = interval(start = diagnosisdate, end = first_drug_date)/
           duration(n=1, units = "months")) %>% 
  mutate(days_at_surg = interval(start = diagnosisdate, end = surgerydate)/
           duration(n=1, units = "months")) %>% 
  ungroup()

```
We have `r drugs1 %>% filter(days_at_first_drug < 0) %>% distinct(patientid) %>% nrow()` patients with date of drug before diagnosis and `r drugs1 %>% filter(days_at_surg < 0) %>% distinct(patientid) %>% nrow()` patients with a date of surgery before diagnosis. Patients left :

@@

### step 2: 60 days rule between diagnosis and treatment
60 days rule between diagnosis and treatment to eliminate patients who didn't get treatment for 60 days which could mean they were treated but it is not recorded. Patients left :
```{r}
remove_60daysrule <- drugs1 %>% 
  filter((days_at_first_drug > 60 | days_at_surg > 60)) %>% 
  distinct(patientid)
remove_60daysrule <- paste(remove_60daysrule$patientid, collapse = "|")

@@

### step 3: 30 days rule excluding patient whith less than 30 days between diagnosis and death
```{r}
drugs1 %>% 
  mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/
           duration(n=1, units = "days"), 
         thirty_days_exclusion = case_when(
           thirty_days_exclusion <= 30                  ~ "Exclude"
         )) %>% 
  filter(thirty_days_exclusion == "Exclude") %>% 
  distinct(patientid) %>% 
  nrow

drugs11 <- drugs1 %>% 
  mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/
           duration(n=1, units = "days"), 
         thirty_days_exclusion = case_when(
           thirty_days_exclusion <= 30                  ~ "Exclude",
           thirty_days_exclusion > 30                   ~ "Include",
           is.na(dateofdeath)                           ~ "Include"
         )) %>% 
  filter(thirty_days_exclusion != "Exclude")

drugs11 %>% distinct(patientid) %>% nrow()

```
In the data, `r drugs1 %>% mutate(thirty_days_exclusion = interval(start = diagnosisdate, end = dateofdeath)/duration(n=1, units = "days"), thirty_days_exclusion = case_when(thirty_days_exclusion <= 30~ "Exclude")) %>% filter(thirty_days_exclusion == "Exclude") %>% distinct(patientid) %>% nrow` are excluded so we still have `r drugs11 %>% distinct(patientid) %>% nrow()` patients.

### step 3: Remove linename that doesn't include platin or taxels in first line -> later in the process, need first to recode linenumber with all the drugs in.
```{r}
# drugs1 <- drugs1 %>% 
#   # 2. Filtering----
#   filter(episodedatasource == "Administrations" & 
#            # ismaintenancetherapy == "FALSE" & 
#            !is.na(amount) &
#            (days_at_first_drug < 60 | days_at_surg < 60) &
#            
#            days_at_first_drug >= 0 &
#            (is.na(surgerydate) | days_at_surg >= 0)
#          )

@@

### step 4: Combine multiple administrations of the same drug at the same date
```{r combine amount same drug one day}
drugs1 <- drugs1 %>% 
  #When want to remove patients who didn't have taxel/platin as 1st line -> remove 260 patients
  # filter(!(linenumber == 1 & !str_detect(linename, "taxel|platin"))) %>% 
  # filter(str_detect(drugname, "taxel|platin") & str_detect(route, "venous|peritoneal")) %>% ############## LATER------------!!!!!
  select(-c(enhancedcohort, episodedatasource, drugcategory, detaileddrugcategory, route)) %>%

@@

### step 5: Recode linenumber depending on surgery date (Categorize Neo and Adjuavnt)
```{r line coding}
therapy_line <- drugs1 %>% 
  # 4. Define Adjuvant, Neoadjuvant, chemo or surgery----
  mutate(chemotherapy_type = case_when(
    # ismaintenancetherapy == "TRUE"    ~ "maintenance",
    episodedate <= surgerydate        ~ "Neoadjuvant", # F63ABD6AEB12C, F4F7B1C5DF24F intraperitoneal Carboplatin
    episodedate > surgerydate         ~ "Adjuvant",
    is.na(surgerydate) &
      !is.na(episodedate)             ~ "Chemotherapy only",
    !is.na(surgerydate) &
      is.na(episodedate)              ~ "Surgery only"
    )) %>% 
  mutate(chemotherapy_type = factor(chemotherapy_type, levels = c("Neoadjuvant", "Adjuvant", "Chemotherapy only", "Surgery only"))) %>%
  group_by(patientid) %>% 
  mutate(had_neo = ifelse(str_detect(chemotherapy_type, "Neo"), "Yes", NA_character_)) %>% 
  fill(had_neo, .direction = "updown") %>% 
  mutate(had_adj = ifelse(str_detect(chemotherapy_type, "Adj"), "Yes", NA_character_)) %>% 
  fill(had_adj, .direction = "updown") %>% 
  mutate(treatment_sequence = case_when(
    had_neo == "Yes" &
      had_adj == "Yes"                           ~ "neo + surg + adj",
    had_neo == "Yes" &
      is.na(had_adj)                             ~ "neo + surg",
    is.na(had_neo) &
      had_adj == "Yes"                           ~ "surg + adj",
    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
    chemotherapy_type == "Surgery only"          ~ "Surgery only"
  )) %>% 
  mutate(therapy = case_when(
    chemotherapy_type == "Neoadjuvant"           ~ "Upfront Chemo",
    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
    chemotherapy_type == "Surgery only"          ~ "Surgery only",
    is.na(had_neo) &
      had_adj == "Yes"                           ~ "Upfront Surgery"
  )) %>% 
  fill(therapy, .direction = "downup") %>% 
  # mutate(therapy1 = case_when(
  #   chemotherapy_type == "Adjuvant"              ~ "Upfront Surgery",
  # )) %>% 
  # fill(therapy1, .direction = "downup") %>% 
  # mutate(therapy = coalesce(therapy, therapy1)) %>% 
  # select( -therapy1) %>%

@@

### step 6: Remove linename that doesn't include platin or taxels in first line
```{r}
# F0017FB3A8828 starts with gemcitabine then have carbo
therapy_line <- therapy_line %>%
  arrange(patientid, episodedate) %>% 
  mutate(remove_linename_other = case_when(
    linenumber_new == 1 &
      str_detect(linename, "platin|taxel")      ~ "keep",
    linenumber_new == 1 &
      !str_detect(linename, "platin|taxel")     ~ "remove",
  )) %>% 
  group_by(patientid) %>% 
  fill(remove_linename_other, .direction = "down") %>% 
  ungroup() %>% 
  filter(remove_linename_other == "keep") %>% 
  select(-remove_linename_other)

therapy_line %>% 
  filter(linenumber_new == 1) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linename) %>% 
  tbl_summary(sort = list(everything() ~ "frequency"))

We now have `r therapy_line %>% distinct(patientid) %>% nrow()` patients.

#### Number of patient who switch line because of surgery from line 1 to adjuvant line
```{r Number of patient who switch line}
therapy_line %>% 
  mutate(change_line = case_when(
    linenumber == 1 & 
      linenumber_new == 2 &
      chemotherapy_type == "Adjuvant" &
      treatment_sequence == "neo + surg + adj"     ~ 1,
    TRUE                                           ~ 0
  )) %>% 
  arrange(desc(change_line)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(change_line) %>% 
  tbl_summary()

# Problem F0000AD999ABF but would be good for F003F2BEEDB37
therapy_line %>% 
  filter(str_detect(patientid, "F0000AD999ABF|F003F2BEEDB37")) %>% 
  arrange(patientid, episodedate) %>% 
  select(patientid, linenumber, linenumber_new, episodedate, chemotherapy_type)

therapy_line %>% 
  mutate(change_line = case_when(
    linenumber == 1 & 
      linenumber_new == 2 &
      chemotherapy_type == "Adjuvant" &
      treatment_sequence == "neo + surg + adj"     ~ 1,
    TRUE                                           ~ 0
  )) %>% 
  filter(change_line == 1) %>% 
  group_by(patientid) %>% 
  mutate(firstdate = first(episodedate)) %>% 
  mutate(lastdate = last(episodedate)) %>% 
  ungroup() %>% 
  mutate(time_of_switch_line = interval(start = firstdate, end = lastdate) / duration(n =1, units = "days")) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x=time_of_switch_line, fill = ..count..))+
  geom_histogram(binwidth = 7)+
  theme_minimal()+
  ggforce::facet_zoom(xlim= c(0,60), zoom.size = 1) + 
  scale_y_continuous(#breaks=c(0, 50, 100, 150),
                     minor_breaks=c(10, 20, 30, 40)#,
                     #labels = c(0, 50, 100, 150)
  )
```

#### How many lines patient got as Neo
```{r}
therapy_line %>% 
  filter(chemotherapy_type == "Neoadjuvant") %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new) %>% 
  tbl_summary()

@@

### step 7: Remove patients with more than 1 line as Neo -34
```{r}
remove_morethan1_neo <- therapy_line %>% 
  filter(chemotherapy_type == "Neoadjuvant" &
           linenumber_new != 1)
remove_morethan1_neo <- paste(remove_morethan1_neo$patientid, collapse = "|")

@@

### step 8: Remove patients who switch cispl vs carbo # 111 patients Car > Cis F1BF7208F0E96, 34 Cis > Car in neo or adj or chemo
```{r}
# But a lot switch cispl vs carbo # 59 patients Car > Cis F1BF7208F0E96, 32 Cis > Car
therapy_line %>% 
  filter(str_detect(linename, "Car") &
           drugname == "cisplatin") %>%
  distinct(patientid) %>% nrow()

@@

<span style="color:red">**Should I do the same between paclitaxel and docetaxel?**</span>

Remember that I coded "paclitaxel" == "paclitaxel protein bound"

If a patient had carbo, pacli, carbo, pacli, docetaxel in a Carboplatin-Paclitaxel line : It makes the coding for cycle number more difficult

I think it would be worth it and this operation would remove these patients:

```{r}
# But a lot switch cispl vs carbo # 59 patients Car > Cis F1BF7208F0E96, 32 Cis > Car
therapy_line %>% 
  filter(str_detect(linename, "Pacli") &
           drugname == "docetaxel") %>%
  distinct(patientid) %>% nrow()
therapy_line %>% 
  filter(str_detect(linename, "Doce") &
           drugname == "Paclitaxel") %>%
  distinct(patientid) %>% nrow()
```
<br>

`r emo::ji("question_mark")`  
<span style="color:red">**Random question : within 1 cycle we can have taxel multiple times, is it possible for carboplatin or cisplatin?**</span>

### step 9: Code cycle
```{r cycle coding}
# Code cycle number
therapy_cycle <- therapy_line %>%

@@

### step 10: Bind everything together and calculating target_auc and expected dose

When I bind things together I take the closest date of creatinine, height, weight, BSA, AUC, from the cycle date to calculate `target_auc` and `expected_dose`. it can be days in between or more. 
`r emo::ji("question_mark")`  
<span style="color:red">**Do we need a maximun?**</span>

As you can see on the plots, the gap can be pretty big so :  
<span style="color:red">**Can we take a creatinine value to bind it to a drug when a year long as past between each other?**</span>  
<span style="color:red">**Same question for height, weight, bsa and corresponding AUC**</span>

Precision when binding for AUC I bind the closest with corresponding drugname (Pacli AUC is not bind with Carbo drug)
```{r target_auc and expected dose}
Treatment <- 
  # Merge with creatinine
  left_join(therapy_cycle, creatinine, by = "patientid") %>%
  mutate(interval_creat = abs(interval(start= creat_date, end= cycle_start_date)/                      
                          duration(n=1, unit="days"))) %>% 
  arrange(interval_creat) %>% 
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
           cycle_start_date, .keep_all = TRUE) %>%

@@

### step 11: Exclude exclude == "1" coded by Lauren due to Flatiron rule

@@

`r emo::ji("question_mark")`  
<span style="color:red">**I need confirmation : we calculate 1 RDI per drug per patient for the first (unique) line of neoadjuvant and 1 RDI per drug per patient for the ALL the lines of adjuvant which are not maintenance. Is that correct**</span>

## Calculate RDI by drug by cycle by patient
Here few examples
```{r, rows.print=15, max.print=30}
Frontline <- Treatment %>% 
  # Calculate RDI for each drug per cycle per patients
  mutate(relative_dose_intensity = amount/expected_dose) %>% 
  group_by(patientid, linenumber_new, cycle_drugname,  chemotherapy_type, linestartdate, lineenddate, cycle_increment) %>% 
  summarise(across(relative_dose_intensity, mean, na.rm = TRUE))

Frontline
```

## Calculate RDI by drug by line by patient
Here few examples
```{r, rows.print=15, max.print=30}
Frontline <- Frontline %>% 
  # Calculate RDI for each drug per line per patients
  group_by(patientid, linenumber_new, cycle_drugname,  chemotherapy_type, linestartdate, lineenddate) %>% 
  summarise(across(relative_dose_intensity, mean, na.rm = TRUE))

Frontline
```

## Calculate RDI by drug by patient
Here few examples
```{r, rows.print=15, max.print=30}
Frontline <- Frontline %>% 
  # Calculate RDI for each drug per patients
  group_by(patientid, cycle_drugname, chemotherapy_type) %>% 
  summarise(across(relative_dose_intensity, mean, na.rm = TRUE)) %>% 
  ungroup()

Frontline

Frontline %>% 
  ggplot(aes(x = relative_dose_intensity, fill = cycle_drugname))+
  geom_histogram(alpha = 0.5)+
  theme_minimal()+
  facet_wrap(.~ chemotherapy_type, scales = "free")

Frontline %>% 
  ggplot(aes(x = relative_dose_intensity, y = chemotherapy_type, fill = cycle_drugname))+
  geom_boxplot()+
  geom_vline(xintercept = 1, color = "red")+
  theme_minimal()
```

```{r}
Frontline <- Frontline %>%

  mutate(RDI_grp = case_when(
    relative_dose_intensity < 0.85          ~ "RDI < 0.85",
    relative_dose_intensity >= 0.85         ~ "RDI >= 0.85"
  )) %>% 
  mutate(RDI_grp = factor(RDI_grp, 
                           labels = c("RDI >= 0.85", "RDI < 0.85"))) %>% 
  mutate(RDI_grp1 = case_when(
    relative_dose_intensity < 0.85          ~ "RDI < 0.85",
    relative_dose_intensity >= 0.85         ~ "RDI >= 0.85",
    relative_dose_intensity >= 0.85         ~ "0.85 <= RDI < 1",
    relative_dose_intensity >= 0.85         ~ "1 <= RDI < 1.5",
    relative_dose_intensity >= 0.85         ~ "1.5 <= RDI < 2",
    relative_dose_intensity >= 0.85         ~ "RDI >= 2",
  )) %>% 
  mutate(RDI_grp1 = factor(RDI_grp1, 
                          labels = c("0.85 >= RDI < 1", "0 < RDI < 0.75", "0.75 <= RDI < 0.85", "1 <= RDI < 1.5", 
                                     "1.5 <= RDI < 2", "RDI >= 2"))) %>% 
  # mutate(delay_incare_dx_to_treat = case_when(
  #   str_detect(therapy, "Chemo")     ~ (interval(start = diagnosisdate, end = episodedate)/
  #     duration(n=1, units = "days")),
  #   str_detect(therapy, "Surgery")   ~ (interval(start = diagnosisdate, end = surgerydate)/
  #     duration(n=1, units = "days"))
  # )) %>% 
  # group_by(patientid) %>% 
  # mutate(first_treatment_date = case_when(
  #   treatment_sequence == "Chemotherapy only"             ~ min(episodedate),
  #   str_detect(treatment_sequence, "neo")                 ~ min(episodedate),
  #   treatment_sequence == "surg + adj"                    ~ surgerydate,
  #   treatment_sequence == "Surgery only"                  ~ surgerydate
  # )) %>% 
  # group_by(patientid) %>% 
  # mutate(first_treatment_date = case_when(
  #   str_detect(therapy, "Chemo")                      ~ min(episodedate),
  #   str_detect(therapy, "Surgery")                    ~ surgerydate,
  # )) %>% 
  # mutate(delay_incare_dx_to_treat = interval(start = diagnosisdate, end = first_treatment_date)/
  #                                         duration(n=1, units = "days")) %>% 
  mutate(month_at_os_from_treatment = interval(start = first_treatment_date, end = followupdate)/
                   duration(n=1, units = "months")) %>% 
  ungroup()

@@
